### 2021-04-19 architecture.tex
Resolve a R2 comment: "locally minimize"

The loss function is clearly differentiable with respect to the symbol costs,
and the symbol cost function $c$ is differentiable with respect to its trainable parameters.
This enables the use of gradient descent to find the values of the parameters of $c$
that minimize the loss value.
\todo[author=R2]{I expect that you mean "to *locally* minimize the loss value". If you do, the fix is simple (just add "locally"); if not, more explanations are needed.}

>>>>

The loss function is clearly differentiable with respect to the symbol costs,
and the symbol cost function $c$ is differentiable with respect to its trainable parameters.
This enables the use of gradient descent to find the values of the parameters of $c$
that locally minimize the loss value.
